\LARGE \bf An Overview of reinforcement learning

### 2020-07-14 paper/paper.tex
Add comments to the algorithms notebooks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

	This electronic document is a ``live'' template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.\todo{Add correct abstract}

\end{abstract}

@@

\todo{}

@@

Conforme la cantidad de visitas incrementa la funcion $V$ converge hacia $v_\pi(s)$;

@@

This is an extension of Q-Learning, that combines it with artificial neural networks. Minh et al showed in \cite{minh_dqn} how a single reinforcement learning agent can achieve high levels of performance in many different problems without relying on different problem-specific feature setes.

Mnih et al. modified the basic Q-learning procedure in three ways. First, they used a method called experience replay. This method stores the agent’s experience at each timestep in a replay memory that is accessed to perform the weight updates. After the game emulator executed action $A_t$ in a state represented by the image stack $S_t$, and returned reward $R_{t+1}$ and image stack $S_{t+1}$, it added the tuple ($S_t$,$A_t$,$R_{t+1}$,$S_{t+1}$) to the replay memory. This memory accumulated experiences over many plays of the same game. At each time step multiple Q-learning updates—a mini-batch—were performed based on experiences sampled uniformly at random from the replay memory. Instead of $S_{t+1}$ becoming the new $S_t$ for the next update as it would in the usual form of Q-learning, a new unconnected experience was drawn from the replay memory to supply data for the next update. Since Q-learning is an off-policy algorithm, it does not need to be applied along connected trajectories.

@@

The principal idea is to split the model in two: one for computing an
action based on a state and another one to produce the $Q$ values of the
action.

@@

\section{Which library or frameworks are the most relevant today?}
\todo{Add library and frameworks}

https://medium.com/data-from-the-trenches/choosing-a-deep-reinforcement-learning-library-890fb0307092

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This document provides an overview of reinforcement learning, this
  is a machine learning technique which deals with the optimization of
  a reward function when the algorithm can only interact with an
  intermediary enviroment. Some general algorithms are shown and the
  most relevant frameworks are discussed. Its current challenges and
  some use cases are also presented.
\end{abstract}

@@

@@

As the number of visits increases, the function $V$ converges to $v_\pi(s)$;

@@

This is an extension of Q-Learning, that combines it with artificial
neural networks. Minh et al showed in \cite{minh_dqn} how a single
reinforcement learning agent can achieve high levels of performance in
many different problems without relying on different problem-specific
feature sets.

Mnih et al.\ modified the basic Q-learning procedure in three
ways. First, they used a method called experience replay. This method
stores the agent’s experience at each timestep in a replay memory that
is accessed to perform the weight updates. After the game emulator
executed action $A_t$ in a state represented by the image stack $S_t$,
and returned reward $R_{t+1}$ and image stack $S_{t+1}$, it added the
tuple ($S_t$,$A_t$,$R_{t+1}$,$S_{t+1}$) to the replay memory. This
memory accumulated experiences over many plays of the same game. At
each time step multiple Q-learning updates—a mini-batch—were performed
based on experiences sampled uniformly at random from the replay
memory. Instead of $S_{t+1}$ becoming the new $S_t$ for the next
update as it would in the usual form of Q-learning, a new unconnected
experience was drawn from the replay memory to supply data for the
next update. Since Q-learning is an off-policy algorithm, it does not
need to be applied along connected trajectories.

@@

The principal idea is to split the deep q-learning model in two: one for computing an
action based on a state and another one to produce the $Q$ values of the
action.

@@

\section{Which library or frameworks are the most relevant today?}
